### 2019-06-12 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
Typo

% Stochastic bandits were historically introduced as a simple model for clinical trials, where arms correspond to some treatments with unknown efficacy \cite{Thompson33}.
% More recently, MAB models have been proved useful for different applications, like cognitive radio, where arms can model the vacancy of radio channels, as presented in Chapter~\ref{chapter:4}, or parameters of a dynamically configurable radio hardware \cite{Maghsudi16,Bonnefoi17,KerkoucheAlami18}.
% Another application is the design of recommender systems, where arms model the popularity of different items (\eg, news recommendation, \cite{Li10}).
%
For cognitive radio applications, as well as other applications such as recommender systems, the assumption that the arms distribution \emph{do not change over time} may be a big limitation.
Indeed, in cognitive radio, new devices can enter or leave the network, which impacts the availability of the radio channel they use to communicate.
And for instance in online recommendation, the popularity of items is also subject to trends.
Hence, there has been some interest on how to take those \emph{non-stationary} aspects into account within a multi-armed bandit model.

@@

\paragraph{Passively adaptive algorithms.}
%
Their common idea is to adapt a classical policy into forgetting old rewards, .
If the forgetting behavior is done efficiently, then the policy can efficiently focus mostly on the most recent rewards, and passively adapt to changes when they happen.
%
The Discounted UCB (D-UCB) algorithm was first introduced in \cite{Kocsis06}, and it is an adaptation of the \UCB{} algorithm, with a discount factor $\gamma\in(0,1)$. It works by decreasing all the past rewards by a multiplicative factor, when receiving a new reward from an arm, so that the recent rewards weight more in the (discounted) empirical mean used for the computation of the \UCB{} indexes.
The regret of D-UCB was proved to be upper-bounded by $\cO(\sqrt{\Upsilon_T T }\log(T))$ in \cite{Garivier11UCBDiscount}, with a tuning $\gamma = 1 - \sqrt{\Upsilon_T/T}/4$, dependent on $\Upsilon_T$.
%
The Sliding-Window UCB (SW-UCB) uses a sliding window of a fixed size $\tau$, to store only the most $\tau$ recent rewards for each arm,
and it was proposed by \cite{Garivier11UCBDiscount}.
They prove that tuning its window-size to $\tau = 2 \sqrt{T\log(T)/\Upsilon_T}$, gives a bound on the regret of SW-UCB of the form $\cO(\sqrt{\Upsilon_T T \log(T)})$.

Both D-UCB and SW-UCB builds on a stationary policy, but for example EXP3.S from \cite{Auer02NonStochastic}
builds on the EXP3 policy, which is designed for the adversarial case.
EXP3.S actually achieves a good regret upper-bound, of the form $\cO(\sqrt{K \Upsilon_T T})$, with no additional prior knowledge except that of $T$ and $\Upsilon_T$.
It constitues a good baseline for our numerical experiments in Section~\ref{sec:6:NumericalExperiments},
even if we did find that EXP3.S performs worse that the most of the other approaches based on extensions of stationary bandit algorithms (\eg, SW-UCB).
% , so we do not include it in .
Similarly, previous works showed that older algorithms have no or weaker regret guarantees, and have been proved to be less efficient empirically, or are designed for more specific settings.

@@

\paragraph{Actively adaptive algorithms.}
%
We distinguish two families,
the first line of research uses frequentist change-point detectors \cite{Basseville93}, combined with stationary policies, usually index policies like \UCB.
When using an efficient CD algorithm with an efficient index policy, these approaches usually perform more efficiently than the passively algorithms.
%
The Adapt-EVE algorithm from \cite{Hartland06} uses a Page-Hikley (PH) Test and the \UCB{} policy, but no theoretical guarantee was given.
%
The Windowed-Mean Shift algorithm from \cite{YuMannor09} is more generic and combines any efficient bandit policy with a CD test based on a sliding window, but there approach is not applicable to the bandit setting of interest in this chapter, as they consider side observations.
%
The EXP3.R algorithm from \cite{Allesiardo15,Allesiardo17} combines a CD algorithm with EXP3, and the history of all arms are reset as soon as a suboptimal arm is detecting to become optimal.
A regret bound of $\cO(\Upsilon_T \sqrt{T \log(T)})$ was proved, even when $\Upsilon_T$ is known.

@@

When all their parameters are tuned correctly, both approaches are proved to achieve a good regret upper-bound, of order $\cO(K \sqrt{\Upsilon_T T \log(K T)})$.
As both results are valid under different assumptions, we consider the two results to be the current state-of-the-art.
As for previous works, tuning their parameters requires to know both the horizon $T$ and the number of breakpoints $\Upsilon_T$, but most importantly it requires a prior knowledge of the problem difficulty, by assuming to know a lower bound on both the length of stationary segments (\eg, $L$ for \MUCB) and on the changes on the means of arms (\eg, $\varepsilon$ for \CUSUM).
%
\CUSUMUCB{} achieves a better regret upper bound, of the order of $\cO(\sqrt{\Upsilon_T T \log(T / \Upsilon_T)})$, but \emph{only} for Bernoulli distributions,
and when its $4$ parameters ($\alpha,\varepsilon,M,h$) are tuned based on problem-dependent knowledge.
%
\MUCB{} achieves a regret bounded by $\cO(\sqrt{\Upsilon_T T \log(T)})$, for bounded distributions, and when its $4$ parameters ($\alpha,w,b,\gamma$) are also tuned based on a problem-dependent knowledge of $\tilde{\delta}$ and $L$ (see Assumption~1 and Remark~1 in \cite{CaoZhenKvetonXie18}).

@@

A different setting where the quantity of interest is not $\Upsilon_T$ but the total variational budget $V_T$, was introduced by \cite{Besbes14stochastic}, for which they proposed the RExp3 algorithm.
The total variation budget $V_T$ is defined as $\sum_{t=1}^{T-1} \sum_{k=1}^K D(\nu_k(t), \nu_k(t+1))$, for a certain measure of difference $D$, which measures how much the two distributions of any arm $k$ have changed from time $t$ to time $t+1$.
Two examples can be the total variation distance $\|\cdot\|_{TV}$ or the Kullback-Leibler divergence.
%
The RExp3 algorithm can also be qualified as passively adaptive: it is based on (non-adaptive) restarts of the EXP3 algorithm. Note that this algorithm is introduced for a different setting, where the quantity of interest is not $\Upsilon_T$ but a quantity $V_T$ called the total variational budget (satisfying $\Delta^{\text{change}} \Upsilon_T \leq V_T \leq \Upsilon_T$ with $\Delta^{\text{change}}$ the minimum magnitude of a change-point).
A regret bound of the order of $\cO(V_T^{1/3} T^{2/3})$ is proved, which is weaker than existing results in our setting.

@@

\begin{lemma}\label{lem:6:ConcFirst}
\begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
    Consider a one-dimensional exponential family $\cE$,
    and let $\nu_{\mu}$ be the unique distribution in this family that has mean $\mu$,
    with moment generating function $\phi_\mu(\lambda) = \bE_{X \sim \nu_{\mu}}[e^{\lambda X}]$.
    Let $\kl_{\cE}(\mu,\mu') = \KL(\nu_{\mu},\nu_{\mu'})$ be the divergence function associated to $\cE$.
    Let $(X_i)_{i \in \N^*}$ and $(Y_k)_{i \in \N^*}$ be two independent \iid{} processes, with respective means $\mu$ and $\mu'$, such that
    $\bE[e^{\lambda X_1}] \leq e^{\phi_{\mu}(\lambda)}$ and $\bE[e^{\lambda Y_1}] \leq e^{\phi_{\mu'}(\lambda)}$.
    %
    Denote $\widehat{\mu}_s = \frac{1}{s}\sum\limits_{i=1}^s X_i$ and $\widehat{\mu}'_r = \frac{1}{r}\sum\limits_{i=1}^r Y_k$.
    Then for every $s,r \in \N^*$ we have,
    \begin{small}
        \begin{equation}
            \bP\left(\exists r \in \N^* : s \, \kl_{\cE}\left(\widehat{\mu}_{s},\mu\right) + r \, \kl_{\cE}\left(\widehat{\mu}_r',\mu'\right) > 3\ln(1+\ln(s)) + 3\ln(1+\ln(r)) + 2\cT\left(\frac{x}{2}\right)\right)\leq e^{-x},
        \end{equation}
    \end{small}
    where $\cT$ is the function defined in \eqref{def:6:function_T}.
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}
\begin{smallproof}
    This Lemma~\ref{lem:6:ConcFirst} is proved in Appendix~\ref{app:6:proofConcFirst}.
\end{smallproof}

@@

\begin{lemma}\label{lem:6:Delay}
\begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
    Let be $\bP_{\mu_0,\mu_1,\tau}$ a probabilistic model under which $X_t \in [0,1]$, and $X_t$ has an average of $\mu_0$ for all $t \leq \tau$, and $\mu_1$ for all $t > \tau$, with $\mu_0 \neq \mu_1$,
    and let $\Delta = |\mu_0 - \mu_1|$.\\
    Then the B-GLRT test given in Definition~\ref{def:6:GLRDef} satisfies
    \begin{equation}
        \bP_{\mu_0,\mu_1,\tau} (\widehat{\tau}_{\delta} \geq \tau + u) \leq \exp\left( -\frac{2\tau u}{\tau + u}\left(\max\left[ 0, \Delta - \sqrt{\frac{\tau + u}{2\tau u} \beta(\tau + u,\delta)} \right]\right)^2 \right).
    \end{equation}
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}
%
\begin{smallproof}
    It is actually not used as such in the proofs of the regret upper bounds given below, because a similar but more specific result is used and proved in the proofs.
    For instance, see below in Section~\ref{par:6:controllingDelayInOneProof} in page~\pageref{par:6:controllingDelayInOneProof}.
    % \TODOL{We have to give the proof, or remove this result? Je ne vois pas le problème de le laisser là, ça formalise le résultat mais on a pas besoin de celui là, ça permet de bien formaliser ce qu'on entend par contrôler le délai, et dans la preuve plus bas on prouve ce qu'on souhaite.}
\end{smallproof}

For a threshold $\beta$ chosen as in the Lemma~\ref{lem:6:FalseAlarm}, we can show that a consequence of the Lemma~\ref{lem:6:Delay} is that if the break-point $\tau$ takes place after $\Delta^{-2} \ln(1/\delta)$ samples, the detection time may be of the same magnitude (with high probability).
%
In other words, if the B-GLRT test observes enough samples before a change-point,
its delay $\widehat{\tau}_\delta$ is in the order of $O(\Delta^{-2} \ln(1/\delta))$, with high probability.

@@

\begin{figure}[h!]
    \centering
    \begin{framed}
    % \begin{small}
    % Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
    % Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
    % \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
    \begin{algorithm}[H]
        % XXX Options
        % \LinesNumbered  % XXX Option to number the line
        % \RestyleAlgo{boxed}
        % XXX Input, data and output
        % \KwIn{\emph{Problem parameters}: $T\in\N^*$, $K\in\N^*$\;}
        \KwIn{\emph{Parameters}: exploration probability $\alpha \in (0, 1)$, confidence level $\delta>0$\;}
        \KwIn{\emph{Option}: \textbf{Local} or \textbf{Global} restart\;}
        % \KwData{Data}
        % \KwResult{Result}
        % XXX Algorithm
        \textbf{Initialization: } $\forall k \in [K]$, $\tau_k = 0$ and $n_k = 0$ \\
        \For{$t=1,2,\dots, T$}{
            \uIf{
                $\alpha>0$ and $t \mod \left\lfloor \frac{K}{\alpha}\right\rfloor \in [K]$
            }{
                $A(t) = t \mod \left\lfloor \frac{K}{\alpha}\right\rfloor$
                \tcp*[f]{forced exploration} \\
            }
            \Else{
                $A(t) = \arg\max\limits_{k \in [K]} \mbox{UCB}_k(t)$ as defined in \eqref{def:6:UCB}
            }
            \mbox{Play arm } $A(t)$ \mbox{and receive the reward } $Y_{A(t),t}$ : $n_{A(t)} = n_{A(t)} + 1; Z_{A(t), n_{A(t)}} = Y_{A(t),t}$ \\
            \uIf(\tcp*[f]{Change point is detected}){
                $\GLR_\delta(Z_{A(t),1}, \dots, Z_{A(t), n_{A(t)}})$ = True
            }
            {
                \uIf{Global restart}{
                    $\forall k\in [K], \tau_k = t$ and $n_k = 0 $.
                    \tcp*[f]{global restart}
                    }
                \Else{
                    $\tau_{A(t)} = t$ and $n_{A(t)} = 0$
                    \tcp*[f]{local restart}
                }
            }
        }
        \caption{\GLRklUCB, with \textbf{Local} or \textbf{Global} restarts}
        \label{algo:6:GLRklUCB}
    \end{algorithm}
    % \end{small}
    \end{framed}
\end{figure}

>>>>

% Stochastic bandits were historically introduced as a simple model for clinical trials, where arms correspond to some treatments with unknown efficacy \cite{Thompson33}.
% More recently, MAB models have been proven useful for different applications, like cognitive radio, where arms can model the vacancy of radio channels, as presented in Chapter~\ref{chapter:4}, or parameters of a dynamically configurable radio hardware \cite{Maghsudi16,Bonnefoi17,KerkoucheAlami18}.
% Another application is the design of recommender systems, where arms model the popularity of different items (\eg, news recommendation, \cite{Li10}).
%
For cognitive radio applications, as well as other applications such as recommender systems, the assumption that the arms distribution \emph{do not change over time} may be a big limitation.
Indeed, in cognitive radio, new devices can enter or leave the network, which impacts the availability of the radio channel they use to communicate.
And for instance in online recommendation, the popularity of items is also subject to trends.
Hence, there has been some interest on how to take those \emph{non-stationary} aspects into account within a multi-armed bandit model.

@@

\paragraph{Passively adaptive algorithms.}
%
Their common idea is to adapt a classical policy into forgetting old rewards, .
If the forgetting behavior is done efficiently, then the policy can efficiently focus mostly on the most recent rewards, and passively adapt to changes when they happen.
%
The Discounted UCB (D-UCB) algorithm was first introduced in \cite{Kocsis06}, and it is an adaptation of the \UCB{} algorithm, with a discount factor $\gamma\in(0,1)$. It works by decreasing all the past rewards by a multiplicative factor, when receiving a new reward from an arm, so that the recent rewards weight more in the (discounted) empirical mean used for the computation of the \UCB{} indexes.
The regret of D-UCB was proven to be upper-bounded by $\cO(\sqrt{\Upsilon_T T }\log(T))$ in \cite{Garivier11UCBDiscount}, with a tuning $\gamma = 1 - \sqrt{\Upsilon_T/T}/4$, dependent on $\Upsilon_T$.
%
The Sliding-Window UCB (SW-UCB) uses a sliding window of a fixed size $\tau$, to store only the most $\tau$ recent rewards for each arm,
and it was proposed by \cite{Garivier11UCBDiscount}.
They prove that tuning its window-size to $\tau = 2 \sqrt{T\log(T)/\Upsilon_T}$, gives a bound on the regret of SW-UCB of the form $\cO(\sqrt{\Upsilon_T T \log(T)})$.

Both D-UCB and SW-UCB builds on a stationary policy, but for example EXP3.S from \cite{Auer02NonStochastic}
builds on the EXP3 policy, which is designed for the adversarial case.
EXP3.S actually achieves a good regret upper-bound, of the form $\cO(\sqrt{K \Upsilon_T T})$, with no additional prior knowledge except that of $T$ and $\Upsilon_T$.
It constitues a good baseline for our numerical experiments in Section~\ref{sec:6:NumericalExperiments},
even if we did find that EXP3.S performs worse that the most of the other approaches based on extensions of stationary bandit algorithms (\eg, SW-UCB).
% , so we do not include it in .
Similarly, previous works showed that older algorithms have no or weaker regret guarantees, and have been proven to be less efficient empirically, or are designed for more specific settings.

@@

\paragraph{Actively adaptive algorithms.}
%
We distinguish two families,
the first line of research uses frequentist change-point detectors \cite{Basseville93}, combined with stationary policies, usually index policies like \UCB.
When using an efficient CD algorithm with an efficient index policy, these approaches usually perform more efficiently than the passively algorithms.
%
The Adapt-EVE algorithm from \cite{Hartland06} uses a Page-Hikley (PH) Test and the \UCB{} policy, but no theoretical guarantee was given.
%
The Windowed-Mean Shift algorithm from \cite{YuMannor09} is more generic and combines any efficient bandit policy with a CD test based on a sliding window, but there approach is not applicable to the bandit setting of interest in this chapter, as they consider side observations.
%
The EXP3.R algorithm from \cite{Allesiardo15,Allesiardo17} combines a CD algorithm with EXP3, and the history of all arms are reset as soon as a suboptimal arm is detecting to become optimal.
A regret bound of $\cO(\Upsilon_T \sqrt{T \log(T)})$ was proven, even when $\Upsilon_T$ is known.

@@

When all their parameters are tuned correctly, both approaches are proven to achieve a good regret upper-bound, of order $\cO(K \sqrt{\Upsilon_T T \log(K T)})$.
As both results are valid under different assumptions, we consider the two results to be the current state-of-the-art.
As for previous works, tuning their parameters requires to know both the horizon $T$ and the number of breakpoints $\Upsilon_T$, but most importantly it requires a prior knowledge of the problem difficulty, by assuming to know a lower bound on both the length of stationary segments (\eg, $L$ for \MUCB) and on the changes on the means of arms (\eg, $\varepsilon$ for \CUSUM).
%
\CUSUMUCB{} achieves a better regret upper bound, of the order of $\cO(\sqrt{\Upsilon_T T \log(T / \Upsilon_T)})$, but \emph{only} for Bernoulli distributions,
and when its $4$ parameters ($\alpha,\varepsilon,M,h$) are tuned based on problem-dependent knowledge.
%
\MUCB{} achieves a regret bounded by $\cO(\sqrt{\Upsilon_T T \log(T)})$, for bounded distributions, and when its $4$ parameters ($\alpha,w,b,\gamma$) are also tuned based on a problem-dependent knowledge of $\tilde{\delta}$ and $L$ (see Assumption~1 and Remark~1 in \cite{CaoZhenKvetonXie18}).

@@

A different setting where the quantity of interest is not $\Upsilon_T$ but the total variational budget $V_T$, was introduced by \cite{Besbes14stochastic}, for which they proposed the RExp3 algorithm.
The total variation budget $V_T$ is defined as $\sum_{t=1}^{T-1} \sum_{k=1}^K D(\nu_k(t), \nu_k(t+1))$, for a certain measure of difference $D$, which measures how much the two distributions of any arm $k$ have changed from time $t$ to time $t+1$.
Two examples can be the total variation distance $\|\cdot\|_{TV}$ or the Kullback-Leibler divergence.
%
The RExp3 algorithm can also be qualified as passively adaptive: it is based on (non-adaptive) restarts of the EXP3 algorithm. Note that this algorithm is introduced for a different setting, where the quantity of interest is not $\Upsilon_T$ but a quantity $V_T$ called the total variational budget (satisfying $\Delta^{\text{change}} \Upsilon_T \leq V_T \leq \Upsilon_T$ with $\Delta^{\text{change}}$ the minimum magnitude of a change-point).
A regret bound of the order of $\cO(V_T^{1/3} T^{2/3})$ is proven, which is weaker than existing results in our setting.

@@

\begin{lemma}\label{lem:6:ConcFirst}
\begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
    Consider a one-dimensional exponential family $\cE$,
    and let $\nu_{\mu}$ be the unique distribution in this family that has mean $\mu$,
    with moment generating function $\phi_\mu(\lambda) = \bE_{X \sim \nu_{\mu}}[e^{\lambda X}]$.
    Let $\kl_{\cE}(\mu,\mu') = \KL(\nu_{\mu},\nu_{\mu'})$ be the divergence function associated to $\cE$.
    Let $(X_i)_{i \in \N^*}$ and $(Y_k)_{i \in \N^*}$ be two independent \iid{} processes, with respective means $\mu$ and $\mu'$, such that
    $\bE[e^{\lambda X_1}] \leq e^{\phi_{\mu}(\lambda)}$ and $\bE[e^{\lambda Y_1}] \leq e^{\phi_{\mu'}(\lambda)}$.
    %
    Denote $\widehat{\mu}_s = \frac{1}{s}\sum\limits_{i=1}^s X_i$ and $\widehat{\mu}'_r = \frac{1}{r}\sum\limits_{i=1}^r Y_k$.
    Then for every $s,r \in \N^*$ we have,
    \begin{small}
        \begin{equation}
            \bP\left(\exists r \in \N^* : s \, \kl_{\cE}\left(\widehat{\mu}_{s},\mu\right) + r \, \kl_{\cE}\left(\widehat{\mu}_r',\mu'\right) > 3\ln(1+\ln(s)) + 3\ln(1+\ln(r)) + 2\cT\left(\frac{x}{2}\right)\right)\leq e^{-x},
        \end{equation}
    \end{small}
    where $\cT$ is the function defined in \eqref{def:6:function_T}.
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}
\begin{smallproof}
    This Lemma~\ref{lem:6:ConcFirst} is proven in Appendix~\ref{app:6:proofConcFirst}.
\end{smallproof}

@@

\begin{lemma}\label{lem:6:Delay}
\begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
    Let be $\bP_{\mu_0,\mu_1,\tau}$ a probabilistic model under which $X_t \in [0,1]$, and $X_t$ has an average of $\mu_0$ for all $t \leq \tau$, and $\mu_1$ for all $t > \tau$, with $\mu_0 \neq \mu_1$,
    and let $\Delta = |\mu_0 - \mu_1|$.\\
    Then the B-GLRT test given in Definition~\ref{def:6:GLRDef} satisfies
    \begin{equation}
        \bP_{\mu_0,\mu_1,\tau} (\widehat{\tau}_{\delta} \geq \tau + u) \leq \exp\left( -\frac{2\tau u}{\tau + u}\left(\max\left[ 0, \Delta - \sqrt{\frac{\tau + u}{2\tau u} \beta(\tau + u,\delta)} \right]\right)^2 \right).
    \end{equation}
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}
%
\begin{smallproof}
    It is actually not used as such in the proofs of the regret upper bounds given below, because a similar but more specific result is used and proven in the proofs.
    For instance, see below in Section~\ref{par:6:controllingDelayInOneProof} in page~\pageref{par:6:controllingDelayInOneProof}.
    % \TODOL{We have to give the proof, or remove this result? Je ne vois pas le problème de le laisser là, ça formalise le résultat mais on a pas besoin de celui là, ça permet de bien formaliser ce qu'on entend par contrôler le délai, et dans la preuve plus bas on prouve ce qu'on souhaite.}
\end{smallproof}

For a threshold $\beta$ chosen as in the Lemma~\ref{lem:6:FalseAlarm}, we can show that a consequence of the Lemma~\ref{lem:6:Delay} is that if the break-point $\tau$ takes place after about $\Delta^{-2} \ln(1/\delta)$ samples, the detection time may be of the same magnitude (with high probability).
%
In other words, if the B-GLRT test observes enough samples before a change-point,
its delay $\widehat{\tau}_\delta$ is in the order of $O(\Delta^{-2} \ln(1/\delta))$, with high probability.

@@

\begin{figure}[h!]
    \centering
    \begin{framed}
    % \begin{small}
    % Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
    % Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
    % \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
    \begin{algorithm}[H]
        % XXX Options
        % \LinesNumbered  % XXX Option to number the line
        % \RestyleAlgo{boxed}
        % XXX Input, data and output
        % \KwIn{\emph{Problem parameters}: $T\in\N^*$, $K\in\N^*$\;}
        \KwIn{\emph{Parameters}: exploration probability $\alpha \in (0, 1)$, confidence level $\delta>0$\;}
        \KwIn{\emph{Option}: \textbf{Local} or \textbf{Global} restart\;}
        % \KwData{Data}
        % \KwResult{Result}
        % XXX Algorithm
        \textbf{Initialization: } $\forall k \in [K]$, $\tau_k = 0$ and $n_k = 0$ \\
        \For{$t=1,2,\dots, T$}{
            \uIf{
                $\alpha>0$ and $t \mod \left\lfloor \frac{K}{\alpha}\right\rfloor \in [K]$\;
            }{
                $A(t) = t \mod \left\lfloor \frac{K}{\alpha}\right\rfloor$\;
                \tcp*[f]{forced exploration} \\
            }
            \Else{
                $A(t) \in \cU\left( \arg\max\limits_{k \in [K]} \mbox{UCB}_k(t) \right)$ as defined in \eqref{def:6:UCB}\;
            }
            \mbox{Play arm } $A(t)$ \mbox{and receive the reward } $Y_{A(t),t}$ : $n_{A(t)} = n_{A(t)} + 1; Z_{A(t), n_{A(t)}} = Y_{A(t),t}$\;
            \uIf(\tcp*[f]{Change point is detected}){
                $\GLR_\delta(Z_{A(t),1}, \dots, Z_{A(t), n_{A(t)}})$ = True
            }
            {
                \uIf{\textbf{Global} restart}{
                    $\forall k\in [K], \tau_k = t$ and $n_k = 0$\;
                    \tcp*[f]{restart all arms}
                    }
                \Else{
                    $\tau_{A(t)} = t$ and $n_{A(t)} = 0$\;
                    \tcp*[f]{restart only this arm}
                }
            }
        }
        \caption{\GLRklUCB, with \textbf{Local} or \textbf{Global} restarts}
        \label{algo:6:GLRklUCB}
    \end{algorithm}
    % \end{small}
    \end{framed}
\end{figure}

### 2019-06-12 2-Chapters/Conclusion/conclusion.tex
Typo

\TODOL{Je dois faire quelques phrases résumant la thèse}

@@

We started to present the multi-armed bandit model, with a finite number of arms and real-valued rewards.
Our main focus is on one-dimensional exponential families of distributions, and on stochastic and stationary problems.
The notations used in the manuscript were introduced by showcasing an interactive demonstration published online\footnote{See \href{https://perso.crans.org/besson/phd/MAB\_interactive\_demo/}{\texttt{perso.crans.org/besson/phd/MAB\_interactive\_demo/}}}.

@@

The second chapter of Part~\ref{part:MABIOT} of this manuscript studied Multi-Players Multi-Arm Bandits models.
%
We present three variants of this model,
with different level of feedback being available to the decentralized players, under which we proposed efficient algorithms.
For the two easiest models --with sensing--, our theoretical contribution improves the state-of-the-art upper bounds on the regret. In the absence of sensing, we also provide some motivation for the practical use of the \Selfish{} heuristic, a simple index policy based on hybrid indices that are directly taking  into account the collision information.
%
We also reviewed various variants of this model, and for some interesting variants we discussed the related literature, which has proved to be very active in the last two years.
For some of these variants, we explained why our approach does not work efficiently without modifications, but we detailed and illustrated how to adapt \MCTopM{} to other settings.
For example, it assumes to know the number of players $M$ before-hand, but we illustrated that previously introduced technique to estimate $M$ can also be applied to our proposal and give satisfactory empirical performances.
% Further works would be required to adapt the theoretical analysis to these various extensions.

>>>>

\TODOL{Je dois faire quelques phrases résumant la thèse, mais plus court}

@@

We started to present the multi-armed bandit model, with a finite number of arms and real-valued rewards.
Our main focus is on one-dimensional exponential families of distributions, and on stochastic and stationary problems.
The notations used in the manuscript were introduced by showcasing an interactive demonstration\footnote{See \href{https://perso.crans.org/besson/phd/MAB\_interactive\_demo/}{\texttt{perso.crans.org/besson/phd/MAB\_interactive\_demo/}}}.

@@

The second chapter of Part~\ref{part:MABIOT} of this manuscript studied Multi-Players Multi-Arm Bandits models.
%
We present three variants of this model,
with different level of feedback being available to the decentralized players, under which we proposed efficient algorithms.
For the two easiest models --with sensing--, our theoretical contribution improves the state-of-the-art upper bounds on the regret. In the absence of sensing, we also provide some motivation for the practical use of the \Selfish{} heuristic, a simple index policy based on hybrid indices that are directly taking  into account the collision information.
%
We also reviewed various variants of this model, and for some interesting variants we discussed the related literature, which has proven to be very active in the last two years.
For some of these variants, we explained why our approach does not work efficiently without modifications, but we detailed and illustrated how to adapt \MCTopM{} to other settings.
For example, it assumes to know the number of players $M$ before-hand, but we illustrated that previously introduced technique to estimate $M$ can also be applied to our proposal and give satisfactory empirical performances.
% Further works would be required to adapt the theoretical analysis to these various extensions.
